Hybrid platforms and bargaining

### 2023-04-16 src/presentation/topics_talk.qmd
Add a preview of results to the introduction

>>>>

## Preview of results

::: {.fragment}
 - The effects of hybrid platforms depend on the substitutability of the products
   - When they are substitutes, it increases the platform's profit share and decreases the fringe's profits
   - In the presence of an investment cost, it leads to lower fringe entry
   - With Logit-demand, hybrid operation leads to welfare losses
:::
::: {.fragment}
 - This modeling strategy seems promising
   - The model is surprisingly tractable
   - Quite general results can be obtained
:::
